Analysing Melbourne CBD pedestrian counts data with a focus on imputation methods

### 2017-10-20 thesis/draft.Rmd
need to add: abstract, updated introduction, motivation, lit review,  completed predictive model section with glm justification, conclusion, references

---
title: "Thesis Draft"
author: "Gavin Chin"
date: "21 September 2017"
output:
  pdf_document: default
  html_document: default
  word_document: default
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE,
                      message = FALSE, warning = FALSE,
                      fig.pos = 'h')
library(tidyverse)
library(lubridate)
library(foreach)
library(doSNOW)
library(rwalkr)
library(pander)
library(RColorBrewer)
library(gridExtra)
library(viridis)
library(ggmap)
set.seed(12345)
```

@@

```{r, fig.width = 8, fig.height=2, fig.cap = "Plot of simulated missingness method 1 at Bourke Street Mall (South)"}
ggplot() + geom_line(aes(x = dfa2$Date_Time, y = mall_missing_1),
                     size = 0.1, alpha = 1) +
           labs(y = "Pedestrian Count", x = "Time and Date",
                title = "Simulated Missingness 1") +
          theme_minimal() + theme(plot.title = element_text(hjust = 0.5))
```

@@

>>>>

---
title: "Analysing Melbourne CBD pedestrian counts data with a focus on imputation methods"
author: "Gavin Chin"
date: "21 September 2017"
output:
  pdf_document: default
  html_document: default
  word_document: default
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE,
                      message = FALSE, warning = FALSE,
                      fig.pos = 'h')
library(tidyverse)
library(lubridate)
library(foreach)
library(doSNOW)
library(rwalkr)
library(pander)
library(RColorBrewer)
library(gridExtra)
library(viridis)
library(ggmap)
library(broom)
set.seed(12345)
```

@@

```{r, fig.width = 8, fig.height=2, fig.cap = "Plot of simulated missingness method 1 at Bourke Street Mall (South). 20% of the observations are removed from the traning data for the imputation model at random."}
ggplot() + geom_line(aes(x = dfa2$Date_Time, y = mall_missing_1),
                     size = 0.1, alpha = 1) +
           labs(y = "Pedestrian Count", x = "Time and Date") +
          theme_minimal() + theme(plot.title = element_text(hjust = 0.5))
```

@@

Using a GLM predicts well compared to estimating with other models such as AR(p) or other time series models when considering the tradeoff between model complexity and prediction accuracy.

As 
```{r, fig.width=6, fig.height=4}
ggplot(dfa2 %>%
         mutate(Date = date(Date_Time))) +
  geom_path(aes(x = as.integer(Time), y = `Melbourne Central`,
                group = Date, colour = Month),
            alpha = 0.1) +
  scale_colour_viridis(discrete = TRUE, option = "C") +
  facet_wrap(~ DayType) + theme_minimal() +
  theme(legend.position = "none") +
  labs(x = "Time of Day", y = "Pedestrian Counts \n at Melbourne Central")
```

```{r, fig.height=4, fig.width=8, fig.cap=paste("Plot of the estimated coefficients of the GLM at each sensor for each variable. Variables (x-axis) is ordered by the scagnostic measure, Outlying.")}
dfcoeff <- data.frame(terms = factor(), coeff = numeric(), sensor = factor())
for(i in names(pred_model)){
  terms <- names(coef(pred_model[[i]]))
  coeff <- coef(pred_model[[i]])
  sensor <- rep(i, length(terms))
  df_b <- data.frame(terms, coeff, sensor)
  dfcoeff <- bind_rows(dfcoeff, df_b)
}
dfcoeff <- dfcoeff %>% spread(terms, coeff)

library(GGally)
library(scagnostics)
ggparcoord(dfcoeff[, -1],
           order = "Outlying", alphaLines = 0.3)
```
